
---
title: "Reproductible Research"
author: "yp"
date: "10 janvier 2016"
output: html_document
---


## Loading and preprocessing the data

```{r}
library(data.table)
library(ggplot2)
unzip(zipfile = "./activity.zip")
hh<-read.csv("activity.csv")
hh<-data.table(hh)
hh$date<-as.Date(hh$date)
```

## What is mean and median total number of steps taken per day?

-Histogram of daily steps

```{r}

DailySteps<-hh[,sum(steps), by="date"]
colnames(DailySteps)<-c("date","steps")
qplot(steps, data=DailySteps, main="number of daily steps")+geom_histogram()
```

-Mean

```{r}


mean(DailySteps$steps, na.rm = TRUE)

```

-Median

```{r}
median(DailySteps$steps, na.rm = TRUE)
```

## What is the average daily activity pattern?

Activity by Day

```{r}
aa<-merge(hh,DailySteps, by="date")
plot(aa$date, aa$steps.y, type="l", xlab="date",ylab="Daily steps",main="Daily activity pattern")
```

Activity by interval:

```{r}
ActivityByInterval<-hh[,mean(steps, na.rm=TRUE), by="interval"]

plot(ActivityByInterval$interval, ActivityByInterval$V1, type="l",xlab="interval",ylab="Average number of setps",main="Daily activity pattern by interval")
```


Interval with maximum activity:
```{r}
ActivityByInterval[which.max(ActivityByInterval$V1)]
```

## Imputing missing values

Number of missing values:

```{r}
sum(is.na(hh$steps))
```

Missing values are replaced by average value of steps (accross all days) for corresponding interval

```{r}

for (i in 1:nrow(hh))
{if (is.na(hh[i]$steps))
{ t<-hh[i]$interval
t2<-ActivityByInterval[interval==t] 
hh[i]$steps=as.integer(t2$V1)

}
}

```

New mean:

```{r}
DailySteps<-hh[,sum(steps), by="date"]
colnames(DailySteps)<-c("date","steps")

mean(DailySteps$steps)

```

Mean is not so different because we have included data that have roughly the same value (average) as non missing values


## Are there differences in activity patterns between weekdays and weekends?

```{r}
hh$day<-ifelse((weekdays(hh$date)=="samedi")|(weekdays(hh$date)=="dimanche"), "weekend", "weekdays")

hh1<-subset(hh, hh$day=="weekdays")
hh2<-subset(hh, hh$day=="weekend")

bb1<-hh1[,mean(steps), by="interval"]
bb2<-hh2[,mean(steps), by="interval"]

par(mfcol=c(1,2))

plot(bb1$interval,bb1$V1, type="l", xlab="interval", ylab="average number of steps", main="activity pattern of week days")
plot(bb2$interval,bb2$V1, type="l", xlab="interval", ylab="average number of steps", main="activity pattern of weekends")

```

On week days, acitivity start earlier in the morning and  there is a very striking peak of steps in the morning. On week ends, activity starts later and is more evenly spread over the day 
